### 2021-01-26 README.Rmd
Update readme.rmd with '*' contribution definition
Updated with DOI for BMC Biology manuscript

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <DOI pending>

Our pre-print is online here:

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells* biorxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.1101/2020.05.05.077362>

>>>>

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <https://doi.org/10.1186/s12915-020-00947-5> 
>
> <sup>*indicates equal contribution</sup>
